names(pf)

### histogram
``` {r}
qplot(x = dob_day, data = pf) +
  scale_x_discrete(breaks=1:31) +
  facet_wrap(~dob_month, ncol = 4)
```

### Friend Count
``` {r}
qplot( x = friend_count, data = pf, xlim = c(1, 1000))

qplot( x = friend_count, data = pf) +
  scale_x_continuous(limits = c(0, 1000))
```


### Adjusting the Bin Width
```{r}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))

```
## Gender
### Omitting NA Gender
```{r}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)

```
#### This omitting all possilbe NAs in different fields.
```{r}
qplot(x = friend_count, data = na.omit(pf), binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```


### Statistic 'by Gender
```{r}
table(pf$gender)
by(pf$friend_count, pf$gender, summary)
```


## Tenure
```{r}
qplot(x = tenure/365, data = pf, binwidth = .25,
      xlab = 'Number of uears using Facebook',
      ylab = 'Number of users in sample',
      color = I('black'), fill = I('#F79420')) +
      scale_x_continuous(breaks = seq(1, 7, 1), limit = c(0, 7))
```


## User Ages
```{r}
qplot(x = age, data = pf, binwidth = 1,
      xlab = "Age of users using Facebook",
      ylab = "Number of users in sample",
      color = I('black'), fill = I('#DA9420')) +
  scale_x_discrete(breaks = seq(0, 113, 5))
```


## Transforming Data
```{r}
p1 = qplot(x = friend_count, data = pf,
           color = I('black'), fill = I('#fd80c3'))

p2 = qplot(x = log10(friend_count + 1), data = pf,
           color = I('blue'), fill = I('#e87129'))

p3 = qplot(x = sqrt(friend_count + 1), data = pf,
           color = I('blue'), fill = I('#e87129'))

grid.arrange(p1, p2, p3, ncol = 1)

summary(pf$friend_count)

summary(log10(pf$friend_count + 1))

summary(sqrt(pf$friend_count))
```

```{r}
p1 <- ggplot(aes(x = friend_count), data = pf) + geom_histogram()
p2 <- p1 + scale_x_log10()
p3 <- p1 + scale_x_sqrt()
grid.arrange(p1, p2, p3, ncol = 1)
```

## Frequency Polygons 
```{r}
qplot(x = friend_count, data = subset(pf, !is.na(pf$gender)), 
      binwidth = 10) +
  scale_x_continuous(lim = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_grid(~gender)
```
```{r}
qplot(x = friend_count, y = ..count../sum(..count..),
      data = subset(pf, !is.na(pf$gender)), 
      xlab = 'Friend Count',
      ylab = 'Proportion of Users with that friend count',
      binwidth = 10, geom = 'freqpoly', color = gender) +
  scale_x_continuous(lim = c(600, 1000), breaks = seq(600, 1000, 10))
```

```{r}
qplot(x = www_likes, y = ..count../sum(..count..),
      data = subset(pf, !is.na(pf$www_likes)), 
      xlab = 'Friend Count',
      ylab = 'Proportion of Users with that www_like',
      geom = 'freqpoly', color = gender) +
  scale_x_continuous() +
  scale_x_log10()
```

### www_like
```{r}
qplot(x = www_likes, data = subset(pf, !is.na(pf$gender)),
      geom = 'freqpoly', color = gender) +
  scale_x_continuous(lim = c(0, 10), breaks = seq(0, 10, 5))
```


```{r}
by(pf$www_likes, pf$gender, sum)
```


```{r}
qplot(x = gender, y = friend_count,
      data = subset(pf, !is.na(gender)),
      geom = 'boxplot') +
  scale_y_continuous(limit = c(0, 1000))
```

```{r}
qplot(x = gender, y = friend_count,
      data = subset(pf, !is.na(gender)),
      geom = 'boxplot', ylim = c(0, 1000))
```

```{r}
qplot(x = gender, y = friend_count,
      data = subset(pf, !is.na(gender)),
      geom = 'boxplot') +
  coord_cartesian(ylim = c(0, 1000))

by(pf$friend_count, pf$gender, summary)
```

```{r}
qplot( x = gender, y = friendships_initiated,
       data = subset(pf, !is.na(gender)),
       geom = 'boxplot') +
  coord_cartesian(ylim = c(0, 500))
```

## Getting Logical
```{r}
summary(pf$mobile_likes)

summary(pf$mobile_likes > 0)

mobile_check_in <- NA

pf$mobile_check_in <- ifelse(pf$mobile_likes > 0, 1, 0)
pf$mobile_check_in <- factor(pf$mobile_check_in)
summary(pf$mobile_check_in)

sum(pf$mobile_check_in == 1) / length(pf$mobile_check_in)
```

## Scatter Plot
```{r}
qplot(x = age, y = friend_count, data = pf)

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20) +
  xlim(13, 90)

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/20) +
  xlim(13, 90)

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim(13, 90) +
  coord_trans(y = "sqrt")

summary(pf$age)
```

## Conditional Means
```{r}
## run first time
# install.packages('dplyr')
# library(dplyr)

age_group <- group_by(pf, age)

pf.fc_by_age <- summarise(age_group, 
          friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n = n())

pf.fc_by_age <- arrange(pf.fc_by_age)

head(pf.fc_by_age)
```

## Conditional Means Alternate Code
```{r}
pf.fc_by_age <- pf %>% 
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n = n()) %>%
  arrange(age)

head(pf.fc_by_age)
```


## Plot mean friend count vs. age using a line graph
```{r}
ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age) +
  geom_line() 
```


## Overlaying Summaries with Raw Data
```{r}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  xlim(13, 90) +
  geom_point(alpha = 1/20, 
             position = position_jitter(h = 0),
             color = 'orange') +
  coord_trans(y = "sqrt") +
  geom_line(stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = quantile, probs = .1,
            linetype = 2, color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, probs = .5,
            color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, probs = .9,
            linetype = 2, color = 'blue')
```